Flowchart of Current Algorithm

### 2009-02-05 docs/flowchart/flowchart.tex
add where we compute gravity in the main algorithm
more div_etarho updates
more div_etarho cleanup

\item We replaced {\bf Correct Base} with $\rho_0 = {\rm{\bf Avg}}(\rho)$ in 
plane-parallel and $\rho_0 = \rho_0 + {\rm{\bf Avg}}(\rho - \rho_0)$ in spherical,
eliminating the need for $\nabla\cdot\etarho$.

@@

\item {\bf React State}$[\rho^n, (\rho h)^n, X_k^n, T^n, (\rho\Hext)^n]
                   \rightarrow$ $[ \rho^{(1)}, (\rho h)^{(1)}, X_k^{(1)}, T^{(1)},
                                  (\rho \omegadot_k)^{(1)}, (\rho \Hnuc)^{(1)} ].$
\item
\begin{description}

\item[plane-parallel:] Set $(\rho h)_0^{n} = \overline{(\rho h)^{(1)}}$.

\item[spherical:] Set $(\rho h)_0^{n} = (\rho h)_0^{n} + {\rm{\bf Avg}}\left[(\rho h)^{(1)} - (\rho h)_0^{n}\right]$.

@@

\item Define an edge-centered $\etarho^{\nph,\star}$ and  cell-centered 
$(\nabla\cdot\etarho\er)^{\nph,\star}$:

\begin{description}
\item[plane-parallel:]~

\begin{equation}
 \etarho^{\nph,\star} =  {\rm {\bf Avg}} \sum_k \left[ \left(\uadvone \cdotb \er + w_0^{\nph,\star}\right) (\rho X_k)^{(1),\nph,\star} \right] - w_0^{\nph,\star} \rho_0^{\nph,\star,{\rm pred}} \enskip ,
\end{equation}
\begin{equation}
(\nabla\cdot\etarho\er)_j^{\nph,\star} = 
\frac{\eta_{\rho,j+\myhalf}^{\nph,\star}-\eta_{\rho,j-\myhalf}^{\nph,\star}}{\Delta r} \enskip ,
\end{equation}

@@

\item {\bf Correct Base}$[\rho_0^{(2a),\star}, (\nabla\cdot\etarho\er)^{\nph,*}] \rightarrow [\rho_0^{n+1,\star}]$.

@@

\item Define an edge-centered $\etarho^{\nph}$ and cell-centered 
$(\nabla\cdot\etarho\er)^{\nph}$:

@@

\begin{equation}
 \etarho^{\nph} = {\rm {\bf Avg}} \sum_k \left [\left(\uadvtwo \cdotb \er + w_0^{\nph}\right) (\rho X_k)^{(1),\nph} \right] - w_0^{\nph} \rho_0^{\nph,{\rm pred}} \enskip ,
\end{equation}
\begin{equation}
(\nabla\cdot\etarho\er)_j^{\nph} = \frac{\eta_{\rho,j+\myhalf}^{\nph} - \eta_{\rho,j-\myhalf}^{\nph}}{\Delta r} \enskip , \\
\end{equation}

@@

\item {\bf Correct Base}$[\rho_0^{(2a)}, (\nabla\cdot\etarho\er)^{\nph}] \rightarrow [\rho_0^{n+1}]$

>>>>

\item We replaced {\bf Correct Base} with $\rho_0 = {\rm{\bf Avg}}(\rho)$ in 
plane-parallel and $\rho_0 = \rho_0 + {\rm{\bf Avg}}(\rho - \rho_0)$ in spherical,
eliminating the need for $\nabla\cdot\etarho$.  {\bf Correct Base} is now used
analogously for setting $(\rho h)_0$ after {\bf React State}.

@@

\item {\bf React State}$[\rho^n, (\rho h)^n, X_k^n, T^n, (\rho\Hext)^n]
                   \rightarrow$ $[ \rho^{(1)}, (\rho h)^{(1)}, X_k^{(1)}, T^{(1)},
                                  (\rho \omegadot_k)^{(1)}, (\rho \Hnuc)^{(1)} ].$

\item {\bf Correct Base}$[(\rho h)_0^{n},(\rho h)^{(1)}] \rightarrow [(\rho h)_0^{n}]$.

@@

\item Define an edge-centered $\etarho^{\nph,\star}$:

\begin{equation}
 \etarho^{\nph,\star} =  {\rm {\bf Avg}} \sum_k \left[ \left(\uadvone \cdotb \er + w_0^{\nph,\star}\right) (\rho X_k)^{(1),\nph,\star} \right] - w_0^{\nph,\star} \rho_0^{\nph,\star,{\rm pred}} \enskip ,
\end{equation}

@@

\item {\bf Correct Base}$[\rho_0^{(2a),\star},\rho^{(2),\star}] \rightarrow [\rho_0^{n+1,\star}]$.

\item Update gravity, $g^{n+1,\star} = g(\rho_0^{n+1,\star})$

@@

\item Define an edge-centered $\etarho^{\nph}$:

@@

\begin{equation}
 \etarho^{\nph} = {\rm {\bf Avg}} \sum_k \left [\left(\uadvtwo \cdotb \er + w_0^{\nph}\right) (\rho X_k)^{(1),\nph} \right] - w_0^{\nph} \rho_0^{\nph,{\rm pred}} \enskip ,
\end{equation}

@@

\item {\bf Correct Base}$[\rho_0^{(2a)},\rho^{(2)}] \rightarrow [\rho_0^{n+1}]$.

\item Update gravity, $g^{n+1} = g(\rho_0^{n+1})$; $g^{\nph} = g(\rho_0^\nph)$
